\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Vikram Emany} % Your name
% You can merge both of le line, if you do not have a website.
\address{+44 7885551585 \\ Milton Keynes,UK} 
\address{\href{mailto:vikram.emany@gmail.com}{Gmail} \\ \href{https://www.linkedin.com/in/vikram-emany/}{LinkedIn} \\ 
\href{https://github.com/vemany}{GitHub} }  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Economics graduate seeking full-time roles in Data Analysis or Fintech.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf BSc Economics}, University of Essex (2:1) \hfill {2020 - 2023}\\
Key modules: Econometrics, Algorithmic Game Theory\\ Mathematical Economics and Behavioural Economics.

{\bf A-Levels }, The Hazeley Academy \hfill {2018 - 2020}\\
Grade A in Finance and Mathematics\\Grade B in Economics 
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
%SKILLS SECTION
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills 
& Machine Learning, Data Analysis, Web Development  

\\&  Data Structures and Algorithms, Data Base Management System.\\
Programming Languages & R Studio, MATLAB, Python, Java, C, HTML, CSS, SQL.\\
Frameworks & MySQL, NumPy, Pandas, Matplotlib, Seaborn.\\
Developing Tools & GitHub, VS Code, Jupyter Notebook.\\

\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Private Equity Analyst Internship} \hfill Jan 2023 - June 2023\\
Corbridge Capital \hfill \textit{London,UK}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Increased exposure as an investment broker while working with IPOs, ISAs, and blue chip equity and bonds by creating detailed Information Memorandums.
     \item Gained an insight into the financials of the Mining, ESG/Construction Private Equity sectors. 
 \end{itemize}
 
\textbf{Investment Banking Program} \hfill November 2021\\
JP Morgan \hfill \textit{London}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Improved knowledge of Mergers and Acquisitions, strategic rationale, and general company analysis while\\ working to provide detailed weekly reports.
     \item Learnt key valuation metrics such as DCF, modelling, and forecasting to analyse firms and provide investment recommendations. 
 \end{itemize}

 \textbf{Financial Services and Consulting Internship } \hfill July 2022\\
Bright Network 
 \begin{itemize}
    \itemsep -3pt {} 
     \item Identified risk and potential controls of various business operations, and created reports on introducing\\ government interventions on private companies.
     \item Gained exposure to collaboration and critical thinking skills through various seminars conducted during the internship.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Prediction Model.} {In this project, I use Numpys, Pandas, and Sklearn libraries such as model selection, linear models, and metrics to create a prediction tool that classifies objects as 'rocks' or 'mines', from extracts of data mined from disparate data sources.\\ The predictive nature of this generic code lends itself to varied applications that require data segmentation using partitions and related analysis.}
\end{rSection} 

%----------------------------------------------------------------------------------------
\end{document}
